How is the Brazilian Amazon constructed as a problem at different levels? Amazonian

### 2022-02-11 20220210_Draft.Rmd
#sovdictionaryupdate #codeforrandomsamplecommentedout

- operationalize 1st version of new dictionary.docx.
- solve broader problems mentioned in new dictionary.docx.
- spread context and classify based in new dictionary -> new iteration of random_sample and dictionary improvement at observation=one context level

@@

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|donoo|internacionalizar")

@@

```{r unnest list}
# Here each context match become one data point in the dataset
sum(lengths(Amazon_speeches$context)) # Check the number of passages matched
# Unnest list into a dataframe
AS_long <- Amazon_speeches %>%
  select(president, year, party, title, location, date, fulltext, context) %>% 
  unnest(cols = c(context))
# Run the same dictionary as before but now only assign 1 if any matches and 0 if no matches
# (no multiple matches/counts per observation)
AS_long$sovereignty <- ifelse(stringr::str_detect(AS_long$context, paste0(sovereignty)), 1, 0)
AS_long$development <- ifelse(stringr::str_detect(AS_long$context, paste0(development)), 1, 0)
AS_long$conservation <- ifelse(stringr::str_detect(AS_long$context, paste0(conservation)), 1, 0)
AS_long$other <- ifelse(AS_long$sovereignty == 0 & AS_long$development == 0 & 
                                  AS_long$conservation == 0, 1, 0)
# Visualize totals
tibble::tibble(Sovereignty = sum(AS_long$sovereignty),
               Development = sum(AS_long$development),
               Conservation = sum(AS_long$conservation),
               Other = sum(AS_long$other))
# Still some overlap... 
```

>>>>

- solve broader problems mentioned in new dictionary.docx.

@@

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|donoo|internacionalizar|fronteira")

@@

```{r unnest list}
# Here each context match become one data point in the dataset
sum(lengths(Amazon_speeches$context)) # Check the number of passages matched
# Unnest list into a dataframe
AS_long <- Amazon_speeches %>%
  select(president, year, party, title, location, date, fulltext, context) %>% 
  unnest(cols = c(context))
# Run the same dictionary as before but now only assign 1 if any matches and 0 if no matches
# (no multiple matches/counts per observation)
AS_long$sovereignty <- ifelse(stringr::str_detect(AS_long$context, paste0(sovereignty)), 1, 0)
AS_long$development <- ifelse(stringr::str_detect(AS_long$context, paste0(development)), 1, 0)
AS_long$conservation <- ifelse(stringr::str_detect(AS_long$context, paste0(conservation)), 1, 0)
AS_long$other <- ifelse(AS_long$sovereignty == 0 & AS_long$development == 0 & 
                                  AS_long$conservation == 0, 1, 0)
#set.seed(123)
#random_sample2 <- AS_long %>% sample_frac(.1)
#write.csv(random_sample2, file="random_sample2.csv")

# Visualize totals
tibble::tibble(Sovereignty = sum(AS_long$sovereignty),
               Development = sum(AS_long$development),
               Conservation = sum(AS_long$conservation),
               Other = sum(AS_long$other))
# Still some overlap... 
```
